---
title: "Applied forecasting for business and economics"
author: "Ch2. Time series graphics"
output:
  html_document:
    toc: true
    toc_float: false
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache=TRUE, warning = FALSE, error = FALSE)
library(fpp2)
options(width=50)
```

# Time series in R

## `ts` objects and `ts` function

A time series is stored in a `ts` object in R:

 - a list of numbers
 - information about times those numbers were recorded.

Example

```{r tstable, echo=FALSE, cache=TRUE}
x <- c(123,39,78,52,110)
yr <- 2012:2016
knitr::kable(data.frame(Year=yr,Observation=x), booktabs=TRUE)
```

Turn this into a ts object using the ts() function:

```r
y <- ts(c(123,39,78,52,110), start=2012)
```

For observations that are more frequent than once per year, add a `frequency` argument.

E.g., monthly data stored as a numerical vector `z`:

```r
y <- ts(z, frequency=12, start=c(2003, 1))
```

`ts(data, frequency, start)`

|Type of data |frequency|start example|
|---|---|---|
|Annual           |1 | 1995 |
|Quarterly        |4  |c(1995,2)|
|Monthly          |12 |c(1995,9)|
|Daily            |7 or 365.25 |1 or c(1995,234)|
|Weekly           |52.18 |c(1995,23)|
|Hourly           |24 or 168 or 8,766 | 1 |
|Half-hourly      |48 or 336 or 17,532| 1|


## Australian GDP

```
ausgdp <- ts(x, frequency=4, start=c(1971,3))
```

  * Class: "ts"
  * Print and plotting methods available.

```{r, echo=TRUE}
ausgdp
autoplot(ausgdp)
```

## Residential electricity sales

```{r}
elecsales
autoplot(elecsales)
```

## Class package

```
> library(fpp2)
```

This loads:

  * some data for use in examples and exercises\pause
  * **forecast** package (for forecasting functions)
  * **ggplot2** package (for graphics functions)
  * **fma** package (for lots of time series data)
  * **expsmooth** package (for more time series data)

# Time plots

## Time plots

The weekly economy passenger load on Ansett Airlines between Australia’s two largest cities.

```{r, echo=TRUE}
autoplot(melsyd[,"Economy.Class"]) +
  ggtitle("Economy class passengers: Melbourne-Sydney") +
  xlab("Year") +
  ylab("Thousands")
```

```{r a10, echo=TRUE}
autoplot(a10) + ylab("$ million") + xlab("Year") +
         ggtitle("Antidiabetic drug sales")
```

Clear and increasing trend. There is also a strong seasonal pattern that increases in size as the level of the series increases. The sudden drop at the start of each year is caused by a government subsidisation scheme that makes it cost-effective for patients to stockpile drugs at the end of the calendar year. Any forecasts of this series would need to capture the seasonal pattern, and the fact that the trend is changing slowly.

## Your turn

- Create plots of the following time series: `dole`, `bricksq`, `lynx`, `goog`
- Use `help()` to find out about the data in each series.
- For the last plot, modify the axis labels and title.

### dole

```{r}
autoplot(dole) +
  ggtitle("Unemployment benefits in Australia") +
  ylab("Currency") + xlab("Year")
```

### bricksq

```{r}
autoplot(bricksq) +
  ggtitle("Australian quarterly clay brick production: 1956–1994.") +
  ylab("million units") + xlab("Year")
```

### lynx

```{r}
autoplot(lynx) +
  ggtitle("Annual Canadian Lynx trappings 1821–1934") +
  ylab("Numbers of lynx trappings") + xlab("Year")
```

### goog

```{r}
autoplot(goog) +
  ggtitle("Google Inc") +
  ylab("dollars") + xlab("Year")
```

## Are time plots best?

Half-hourly and daily electricity demand for Victoria, Australia, in 2014

```{r maxtemp}
autoplot(elecdaily[,"Temperature"]) +
  xlab("Week") + ylab("Max temperature")

qplot(time(elecdaily), elecdaily[,"Temperature"]) +
  xlab("Week") + ylab("Max temperature")

data.frame(
  Week = c(time(elecdaily)),
  Maxtemp = c(elecdaily[,"Temperature"]) ) %>%
  ggplot(aes(x=Week, y=1)) +
    geom_tile(aes(fill=Maxtemp)) +
    scale_fill_gradient2(
      low = "navy",
      mid = "yellow",
     high = "red", midpoint=28) +
    ylab("") + scale_y_discrete(expand=c(0,0)) +
  theme(legend.position="bottom")  
```

# Seasonal plots

## Seasonal plots

A seasonal plot is similar to a time plot except that the data are plotted against the individual “seasons” in which the data were observed. An example is given below showing the antidiabetic drug sales.

```{r, echo=TRUE}
ggseasonplot(a10, year.labels=TRUE, year.labels.left=TRUE) +
  ylab("$ million") +
  ggtitle("Seasonal plot: antidiabetic drug sales")
```

  * Data plotted against the individual "seasons" in which the data were observed.  (In this case a "season" is a month.)
  * Something like a time plot except that the data from each season are overlapped.
  * Enables the underlying seasonal pattern to be seen more clearly, and also allows any substantial departures from the seasonal pattern to be easily identified.
  * In R: `ggseasonplot()`

## Seasonal polar plots

Setting polar=TRUE makes the time series axis circular rather than horizontal.

```{r}
ggseasonplot(a10, polar=TRUE) + ylab("$ million") +
  theme(legend.position="bottom")  
```

## Seasonal subseries plots

- The horizontal lines indicate the means for each month
- Seasonal pattern to be seen clearly
- Changes in seasonality over time

An alternative plot that emphasises the seasonal patterns is where the data for each season are collected together in separate mini time plots.

```{r, echo=TRUE}
ggsubseriesplot(a10) + ylab("$ million") +
  ggtitle("Subseries plot: antidiabetic drug sales")
```

  * Data for each season collected together in time plot as separate time series.
  * Enables the underlying seasonal pattern to be seen clearly, and changes in seasonality over time to be visualized.
  * In R: `ggsubseriesplot()`

## Quarterly Australian Beer Production

```{r}
beer <- window(ausbeer,start=1992)
autoplot(beer)

ggseasonplot(beer,year.labels=TRUE)

ggsubseriesplot(beer)
```

## Your turn

The `arrivals` data set comprises quarterly international arrivals (in thousands) to Australia from Japan, New Zealand, UK and the US.

  - Use `autoplot()` and `ggseasonplot()` to compare the differences between the arrivals from these four countries.
  - Can you identify any unusual observations?

```{r}
autoplot(arrivals, year.labels=TRUE, continuous=TRUE) +
  ggtitle("International Arrivals to Australia")  +
  theme(legend.position="bottom")  

# ggseasonplot(arrivals) +
#     ggtitle("International Arrivals to Australia")  
```  

# Seasonal or cyclic?

## Time series patterns

Trend: pattern exists when there is a long-term increase or decrease in the data.

Seasonal: pattern exists when a series is influenced by seasonal factors (e.g., the quarter of the year, the month, or day of the week).

Cyclic: pattern exists when data exhibit rises and falls that are \emph{not of fixed period} (duration usually of at least 2 years).

## Time series components

Differences between seasonal and cyclic patterns:

* seasonal pattern constant length; cyclic pattern variable length
* average length of cycle longer than length of seasonal pattern
* magnitude of cycle more variable than magnitude of seasonal pattern

## Time series patterns

```{r}
autoplot(window(elec, start=1980)) +
  ggtitle("Australian electricity production") +
  xlab("Year") + ylab("GWh")
```

```{r}
autoplot(bricksq) +
  ggtitle("Australian clay brick production") +
  xlab("Year") + ylab("million units")
```

```{r}
autoplot(hsales) +
  ggtitle("Sales of new one-family houses, USA") +
  xlab("Year") + ylab("Total sales")
```

```{r}
autoplot(ustreas) +
  ggtitle("US Treasury Bill Contracts") +
  xlab("Day") + ylab("price")
```

```{r}
autoplot(lynx) +
  ggtitle("Annual Canadian Lynx Trappings") +
  xlab("Year") + ylab("Number trapped")
```

## Seasonal or cyclic?

Differences between seasonal and cyclic patterns:

  * seasonal pattern constant length; cyclic pattern variable length
  * average length of cycle longer than length of seasonal pattern
  * magnitude of cycle more variable than magnitude of seasonal pattern

The timing of peaks and troughs is predictable with seasonal data, but unpredictable in the long term with cyclic data.

# Lag plots and autocorrelation

## Beer production

Scatterplots of quarterly Australian beer production, where the horizontal axis shows lagged values of the time series. Each graph shows $y_t$ plotted against $y_{t-k}$ for different values of $k$. 

```{r}
beer <- window(ausbeer, start=1992)
gglagplot(beer) +
  theme(legend.position="bottom")  
```

## Lagged scatterplots

  * Each graph shows $y_t$ plotted against $y_{t-k}$ for different values of $k$.
  * The autocorrelations are the correlations associated with these scatterplots.

## Autocorrelation

**Covariance** and **correlation**: measure extent of **linear relationship** between two variables ($y$ and $X$).\pause

**Autocovariance** and **autocorrelation**: measure linear relationship between **lagged values** of a time series $y$.\pause

We measure the relationship between:

  * $y_{t}$ and $y_{t-1}$
  * $y_{t}$ and $y_{t-2}$
  * $y_{t}$ and $y_{t-3}$
  * etc.

We denote the sample autocovariance at lag $k$ by $c_k$ and the sample autocorrelation at lag $k$ by $r_k$.  Then define

$c_k &= \frac{1}{T}\sum_{t=k+1}^T (y_t-\bar{y})(y_{t-k}-\bar{y}) \\[0.cm]
\text{and}\qquad
r_{k} &= c_k/c_0$


  * $r_1$ indicates how successive values of $y$  relate to each other
  * $r_2$ indicates how  $y$ values two periods apart relate to each other
  * $r_k$ is **almost** the same as the sample correlation between $y_t$ and $y_{t-k}$.

Results for first 9 lags for beer data:

```{r, echo=FALSE}
beeracf <- matrix(acf(c(beer), lag.max=9,
                      plot=FALSE)$acf[-1,,1], nrow=1)
colnames(beeracf) <- paste("$r_",1:9,"$",sep="")
knitr::kable(beeracf, booktabs=TRUE,
             align="c", digits=3,
             format.args=list(nsmall=3))
```

```{r beeracf, fig.height=2.5}
ggAcf(beer)
```

  * $r_{4}$  higher than for the other lags. This is due to **the seasonal pattern in the data**: the peaks tend to be **4 quarters** apart and the troughs tend to be **2 quarters** apart.
  * $r_2$ is more negative than for the other lags because troughs tend to be 2 quarters behind peaks.
  * Together, the autocorrelations at lags 1, 2, $\dots$, make up the **autocorrelation** or ACF.
  * The plot is known as a **correlogram**

## ACF

Peaks are evry four quarters apart and tend are two quarters apart

```{r, echo=TRUE}
ggAcf(beer)
```

## Trend and seasonality in ACF plots

- When data have a trend, the autocorrelations for small lags tend to be large and positive.
- When data are seasonal, the autocorrelations will be larger at the seasonal lags (i.e., at multiples of the seasonal frequency)
- When data are trended and seasonal, you see a combination of these effects.

## Aus monthly electricity production

```{r, fig.height=3}
elec <- window(elec, start=1980)
autoplot(elec) + xlab("Year") + ylab("GWh")
```

- The data is trended up and seasonal, you see a combination of these effects in acf.

```{r}
ggAcf(elec, lag.max=48)
```

The slow decrease in the ACF as the lags increase is due to the trend, while the “scalloped” shape is due the seasonality.

Time plot shows clear trend and seasonality.

The same features are reflected in the ACF.

  * The slowly decaying ACF indicates trend (updward).
  * The ACF peaks at lags 12, 24, 36, $\dots$, indicate seasonality of length 12.

## Google stock price

```{r}
autoplot(goog)

ggAcf(goog, lag.max=100)
```

  * The slowly decaying ACF indicates trend (upward).

## Your turn

We have introduced the following graphics functions:

  - `gglagplot`
  - `ggAcf`

Explore the following time series using these functions. Can you spot any seasonality, cyclicity and trend? What do you learn about the series?

  - `hsales`
  - `usdeaths`
  - `bricksq`
  - `sunspotarea`
  - `gasoline`
  
### hsales

Period: Monthly

```{r, echo = FALSE}
autoplot(hsales)

ggAcf(hsales)
```

Seasonal and Trend
  * Lag 12 higher than for the other lags
  * The ACF peaks at lags 12, 24, $\dots$, indicate seasonality of length 12.
  * Lag 19 lower than for the other lags
  * Troughs tend to be of length 7
Peaks are every 12 periods apart and tend are 7 periods apart

### usdeaths

Period: Monthly

```{r, echo = FALSE}
autoplot(usdeaths)

ggAcf(usdeaths)
```

Seasonal and Trend
  
  * Lag 12 higher than for the other lags
  * The ACF peaks at lags 12, 24, $\dots$, indicate seasonality of length 12.
  * Lag 6 lower than for the other lags
  * The ACF low peaks at lags 6, 18
  * Troughs tend of length 6 periods apart

Peaks are every 12 periods apart and tend are 6 periods apart

### bricksq

Period: Quarterly

```{r, echo = FALSE}
autoplot(bricksq)

ggAcf(bricksq)
```

Seasonal and Trend
  
  * The slowly decaying ACF indicates trend
  * Lag 4 higher than for the other lags
  * The ACF peaks at lags 4, 8, 12, $\dots$, indicate seasonality of length 4
  * Lag 6 lower than for the other lags
  * The ACF low peaks at lags 2, 6, 10
  * Trend of length 4 periods apart
Peaks are every 4 periods apart and tend are 4 periods apart

### sunspotarea

Period: Annual

```{r, echo = FALSE}
autoplot(sunspotarea)

ggAcf(sunspotarea)
```

Seasonal and Trend
  
  * Lag 10 higher than for the other lags
  * The ACF peaks at lags 10, 21, $\dots$, indicate seasonality of length 10
  * Lag 5 lower than for the other lags
  * The ACF low peaks at lags 5, 16
  * Trend of length 5 periods apart
Peaks are every 10 periods apart and tend are 5 periods apart

### gasoline

Period: Weekly

```{r, echo = FALSE}
autoplot(gasoline)

ggAcf(gasoline)
```

Seasonal and Trend
  * The slowly decaying ACF indicates trend
  
  * Lag 10 higher than for the other lags
  
  * The ACF peaks at lags 50, 105, $\dots$, indicate seasonality of length 50
  
  * The ACF low peaks at lags 25, 80
  
  * Trend of length 25 periods apart
  
Peaks are every 50 periods apart and tend are 25 periods apart

## Which is which?

```{r, echo=FALSE, warning=FALSE}
tp1 <- autoplot(cowtemp) + xlab("") + ylab("chirps per minute") +
  ggtitle("1. Daily temperature of cow")  +
  theme(plot.title = element_text(size = 8))
tp2 <- autoplot(USAccDeaths/1e3) + xlab("") + ylab("thousands") +
  ggtitle("2. Monthly accidental deaths")  +
  theme(plot.title = element_text(size = 8))
tp3 <- autoplot(AirPassengers) + xlab("") + ylab("thousands") +
  ggtitle("3. Monthly air passengers")  +
  theme(plot.title = element_text(size = 8))
tp4 <- autoplot(mink/1e3) + xlab("") + ylab("thousands") +
  ggtitle("4. Annual mink trappings")  +
  theme(plot.title = element_text(size = 8))
acfb <- ggAcf(cowtemp, ci=0) + xlab("") + ggtitle("B") + ylim(-0.4,1) 
acfa <- ggAcf(USAccDeaths, ci=0) + xlab("") + ggtitle("A") + ylim(-0.4,1)
acfd <- ggAcf(AirPassengers, ci=0) + xlab("") + ggtitle("D") + ylim(-0.4,1)
acfc <- ggAcf(mink, ci=0) + xlab("") + ggtitle("C") + ylim(-0.4,1)
gridExtra::grid.arrange(tp1,tp2,tp3,tp4,
                        acfa,acfb,acfc,acfd,nrow=2)
```

Ans: 1-D, 2-B, 3-A, 4-C

# White noise

## Example: White noise

```{r}
set.seed(30)
wn <- ts(rnorm(50))
autoplot(wn) + ggtitle("White noise")
ggAcf(wn)
```

```{r, results='asis', echo=FALSE, include=FALSE}
wnacf <- matrix(acf(c(wn), lag.max=10,
                      plot=FALSE)$acf[-1,,1], nrow=1)
colnames(wnacf) <- paste("$r_{",1:10,"}$",sep="")
print(xtable::xtable(t(wnacf)),
    sanitize.rownames.function=identity,
    booktabs=TRUE,
    include.colnames = FALSE,
    hline.after = FALSE,
    size='small',
    comment=FALSE,
    floating=FALSE)
```

```{r, echo=FALSE, include=FALSE}
# Create nice R figures
savepdf <- function(file, width=16, height=10)
{
  fname <<- paste("figs/",file,".pdf",sep="")
  pdf(fname, width=width/2.54, height=height/2.54, pointsize=10)
  par(mgp=c(2.2,0.45,0), tcl=-0.4, mar=c(3.3,3.6,1.1,1.1))
}
endpdf <- function()
{
  crop::dev.off.crop(fname)
}
savepdf("wnacf")
ggAcf(wn)
endpdf()
```

Sample autocorrelations for white noise series.

We expect each autocorrelation to be close to zero.

## Sampling distribution of autocorrelations

Sampling distribution of $r_k$ for white noise data is asymptotically N(0,$1/T$).\pause

  *  95% of all $r_k$ for white noise must lie within $\pm 1.96/\sqrt{T}$.
  * If this is not the case, the series is probably not WN.
  * Common to plot lines at $\pm 1.96/\sqrt{T}$ when plotting ACF.
These are the \textcolor{orange}{\textbf{\emph{critical values}}}.

## Autocorrelation

Example:

$T=36$ and so critical values at $\pm 1.96/\sqrt{36} = \pm 0.327$.

All autocorrelation coefficients lie within these limits, confirming  that the data are white noise. (More precisely, the data cannot be distinguished rom white noise.)

## Example: Pigs slaughtered

```{r, fig.height=3}
pigs2 <- window(pigs, start=1990)
autoplot(pigs2) +
  xlab("Year") + ylab("thousands") +
  ggtitle("Number of pigs slaughtered in Victoria")

ggAcf(pigs2)
```

Monthly total number of pigs slaughtered in the state of Victoria, Australia, from January 1990 through August 1995. (Source: Australian Bureau of Statistics.)

  * Difficult to detect pattern in time plot.
  * ACF shows some significant autocorrelation at lags 1, 2, and 3.
  * $r_{12}$ relatively large although not significant.  This may indicate some slight seasonality.

These show the series is **not a white noise series**.

## Your turn

You can compute the daily changes in the Google stock price using

```r
dgoog <- diff(goog)
```

Does `dgoog` look like white noise? Ans. It does not.

```{r, , fig.height=3.5, echo=FALSE}
acf(goog)
```

# Exercises

## Exercises 1

Use the help function to explore what the series gold, woolyrnq and gas represent.

- Use autoplot() to plot each of these in separate plots.
- What is the frequency of each series? Hint: apply the frequency() function.
- Use which.max() to spot the outlier in the gold series. Which observation was it?

- gold

```{r, echo=FALSE}
autoplot(gold)
ggAcf(gold)
frequency(gold)
which.max(gold)
```

Period: Daily
Trending downard

- woolyrnq

```{r, echo=FALSE}
autoplot(woolyrnq)
ggAcf(woolyrnq)
frequency(woolyrnq)
which.max(woolyrnq) 
```

Period: Quarterly
Trending downard, Seasonal

- gas

```{r, echo=FALSE}
autoplot(gas)
ggAcf(gas)
frequency(gas)
which.max(gas)
```

Period: Monthly
Trending upward, Seasonal

## Exercises 2

- Read the data into R

```{r}
tute1 <- read.csv("data/tute1.csv", header=TRUE)
```

- Convert the data to time series

```{r}
mytimeseries <- ts(tute1[,-1], start=1981, frequency=4)
```

- Construct time series plots of each of the three series

```{r, echo=FALSE}
autoplot(mytimeseries, facets=TRUE)
```

## Exercises 3

- Read the data into R

```{r}
retaildata <- readxl::read_excel("data/retail.xlsx", skip=1)
```

- Select one of the time series

```{r}
myts <- ts(retaildata[,"A3349873A"], frequency=12, start=c(1982,4))
```

- Explore your chosen retail time series 
- Can you spot any seasonality, cyclicity and trend? What do you learn about the series?

```{r, echo = FALSE}
autoplot(myts)

ggseasonplot(myts) +
  theme(legend.position="bottom")  

ggsubseriesplot(myts)

gglagplot(myts) +
  theme(legend.position="bottom")  
```

Peaks are every 12 periods apart and tend are 6 periods apart

- The slowly decaying ACF indicates trend (updward).
- The ACF peaks at lags 12, 24, $\dots$,indicate seasonality of length 12.

```{r, fig.height=3, echo=FALSE}
ggAcf(myts)
```

## Exercises 4

Create time plots of the following time series: bicoal, chicken, dole, usdeaths, lynx, goog, writing, fancy, a10, h02.

- Use help() to find out about the data in each series.

- For the goog plot, modify the axis labels and title.

## Exercises 5

Use the ggseasonplot() and ggsubseriesplot() functions to explore the seasonal patterns in the following time series: writing, fancy, a10, h02.

- What can you say about the seasonal patterns?

- Can you identify any unusual years?

## Exercises 6

Use the following graphics functions: autoplot(), ggseasonplot(), ggsubseriesplot(), gglagplot(), ggAcf() and explore features from the following time series: hsales, usdeaths, bricksq, sunspotarea, gasoline.

- Can you spot any seasonality, cyclicity and trend?

- What do you learn about the series?

## Exercises 7

The arrivals data set comprises quarterly international arrivals (in thousands) to Australia from Japan, New Zealand, UK and the US.

- Use autoplot(), ggseasonplot() and ggsubseriesplot() to compare the differences between the arrivals from these four countries.

-Can you identify any unusual observations?

## Exercises 9

The pigs data shows the monthly total number of pigs slaughtered in Victoria, Australia, from Jan 1980 to Aug 1995. Use autoplot and ggAcf for mypigs series and compare these to white noise plots from Figures 2.17 and 2.18.

```{r, echo=FALSE}
mypigs <- window(pigs, start=1990)
autoplot(mypigs)
ggAcf(mypigs)
```

## Exercises 10

dj contains 292 consecutive trading days of the Dow Jones Index. Use ddj <- diff(dj) to compute the daily changes in the index. Plot ddj and its ACF. Do the changes in the Dow Jones Index look like white noise?

```{r, echo=FALSE}
ddj <- diff(dj)
autoplot(ddj)
ggAcf(ddj)
```
